---
title: "Missingdata"
author: "IK & YH"
date: "2023-01-06"
format:
  html:
    toc: true
    smooth-scroll: true
    css: ../style.css
    grid: 
      body-width: 1200px
    theme: default
editor: visual
---

## Notwendige Pakete laden und aktivieren

```{r warning=FALSE, message=FALSE, results='hide'}
library(mice)
```

# Beispiel 1:nhanes - NHANES example - all variables numerical

\*Description A small data set with non-monotone missing values.

\*Format A data frame with 25 observations on the following 4 variables.

age - Age group (1=20-39, 2=40-59, 3=60+) bmi - Body mass index (kg/m\*\*2) hyp - Hypertensive (1=no,2=yes) chl - Total serum cholesterol (mg/dL)

\*Details A small data set with all numerical variables. The data set nhanes2 is the same data set, but with age and hyp treated as factors.

\*Source Schafer, J.L. (1997). Analysis of Incomplete Multivariate Data. London: Chapman & Hall.

## Daten laden

```{r}
nhanes <- (nhanes)
nhanes2 <- nhanes2
```

## Muster Missing

```{r}
md.pattern(nhanes)
```

### Incomplete cases

```{r}
ic(nhanes) # get the 12 rows with incomplete cases
ic(nhanes[1:10,]) # incomplete cases within the first ten rows
ic(nhanes[,2:3]) # restrict extraction to variables bmi and hyp
```

## Imputation

```{r}
# do default multiple imputation on a numeric matrixm m=10 imputations
imp <- mice(nhanes, m=10, method = "pmm")
# pmm = predictive mean matching = default

## Zeige Predictormatrix
imp

# list the actual imputations for BMI
imp$imp$bmi

# show first completed data matrix
complete(imp)

# imputation on mixed data with a different method per column
imp2 <- mice(nhanes2, meth=c('sample','pmm','logreg','norm'))
```

## Analysieren der Daten / Modelldefinition und -schaetzung

```{r}
# Definiere Modell für alle Datensätze
fit1 <- with(data=imp,exp=lm(chl~age + bmi + hyp))
# Definiere alternatives Modell für alle Datens
fit2 <- with(data=imp,exp=lm(chl~age + hyp))

# Ergebnisse der Modellschätzungen in den einzelnen Datensätzen
summary(fit1)
summary(fit2)
```

## Poole Ergebnisse ueber Datensaetze hinweg

```{r}
fit1.pooled <- pool(fit1)
fit2.pooled <-pool(fit2)

# Modellzusammenfassungen
summary(fit1.pooled)
summary(fit2.pooled)
```

## Modellvergleiche bei imputierten Daten

```{r}
# Wald t-Test
summary(D1(fit1, fit2))
# Hinweis: riv = relative increase in variance

# likelihood ratio Test
summary(D3(fit1, fit2))
```

## R2 pooled

```{r}
pool.r.squared(fit1)
pool.r.squared(fit1,adjusted=TRUE) # adjustiert
# Hinweis: fmi = fraction of missing information

pool.r.squared(fit2)
pool.r.squared(fit2,adjusted=TRUE) # adjustiert
```

# Beispiel 2: boys - Growth of Dutch boys

Dieses Beispiel ist für graphische Darstellungen. Es zeigt auch, dass berechnete Variablen wie BMI beim imputieren Probleme verursachen können.

\*Description Height, weight, head circumference and puberty of 748 Dutch boys.

\*Format A data frame with 748 rows on the following 9 variables:

age - Decimal age (0-21 years) hgt - Height (cm) wgt - Weight (kg) bmi - Body mass index hc - Head circumference (cm) gen - Genital Tanner stage (G1-G5) phb - Pubic hair (Tanner P1-P6) tv - Testicular volume (ml) reg - Region (north, east, west, south, city)

\*Details Random sample of 10% from the cross-sectional data used to construct the Dutch growth references 1997. Variables gen and phb are ordered factors. reg is a factor.

## Daten laden

```{r}
boys <- (boys)
```

## Missing data pattern

```{r}
md.pattern(boys)
```

## Impute data

```{r}
# create two imputed data sets
imp.boys <- mice(boys, m=2)
# erster imputierter Datensatz
z <- complete(imp.boys, 1)

# create imputations for age <8yrs
plot(z$age, z$gen, col=mdc(1:2)[1+is.na(boys$gen)],
xlab = "Age (years)", ylab = "Tanner Stage Genital")
```

```{r}
# figure to show that the default imputation method does not impute BMI consistently
plot(z$bmi,z$wgt/(z$hgt/100)^2, col=mdc(1:2)[1+is.na(boys$bmi)],
xlab = "Imputed BMI", ylab="Calculated BMI")
```

## Aufgabe

1.  Schließe BMI aus dem Datensatz aus und imputiere Daten erneut
2.  Berechne BMI aus Gewicht und Größe

```{r}

```
